An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-30 poly-embed-journal/poly-embed-journal.tex
Adding proof first pass of Theorem 9 and fixing notation in Appendix

%\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
\begin{definition}[Supports]
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	(i) $P \subseteq H^+$ or $P \subseteq -H^+$, and
	(ii)$H \cap \mathrm{bd}(P) \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \mathrm{bd}(P)$.
\end{definition}

@@

%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
	\jessie{TODO}
	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.	
  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
\end{proof}

@@

Given any $v$ in a given set $\V$, define $H^+_v := H^+_{([v;-1], 0)}$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace.
Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our $\hyp(g_\V)$ to the nonnegative orthant. 
Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;0], 0)}$.

%Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.

@@

Throughout this section let $G:= \hyp(g_V)$ for a fixed finite set $\V$.
Now, we can define $G$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
\begin{claim}\label{claim:G-intersection-H}
  $G = \cap \H$.
\end{claim}
\begin{proof}
  $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$ respectively, so $(x,c) \in \cap \H$.
\end{proof}

@@

\begin{claim}\label{claim:G-full-dimensional}
  $G$ is $d$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
\end{claim}
\begin{proof}
  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
\end{proof}

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet.
\end{lemma}
\begin{proof}
  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}
We can also show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $G$.

\begin{lemma}\label{lem:HY-subset-Hstar}
  $\H_\Y \subseteq \H^*$.
\end{lemma}
\begin{proof}
  If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$ and is concave.
  Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
\end{proof}

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
  Take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ to be the unique set generating $\H_{\V^*}$.
  (Uniqueness of $\V^*$ follows from uniqueness of $\H^*$.)
  The moreover follows since every $H_v \in \H_{\V^*} \subseteq \H^*$ generates a facet.

@@

\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
  Let $\V' \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_{\V'}$ satisfies $G = \cap \H$.  Then $\V^* \subseteq \V'$.
\end{corollary}
\begin{proof}
  $\H_\Y \cup \H_{\V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V'$. \jessiet{Add refs}
\end{proof}

We now show that we can equivalently construct $g$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$.
\begin{claim}\label{claim:g-gen-by-Vstar}
  $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
\end{claim}
\begin{proof}
  $G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
  Since $G$ is the hypograph of $g$, this means $g$ can be written as 
  $g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$. 
\end{proof}

@@

Now suppose $L$ is a minimizable loss function.
For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$, which we assume is polyhedral throughout.
Consider the function $g(x) = \risk{L}_+(x)$.
%As before, take $G$ to be the hypograph of $g$.
We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  
Unlike above, these could be infinite sets.  
Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
\begin{claim}
	$\hyp(g) = \cap\H$.
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(G)
	&\iff g(x) \geq c & \text{ Definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
	& & \text{the inner product with $x$ and minimizable.} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$} \\ 
	\end{align*}
	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g) = \cap \H$.

@@

%\raf{Need to use minimizable}
We can now use the results from \S~\ref{appsubsec:phase1} to conclude that $\hyp(g)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for some unique finite set $\V^*$.
Moreover, we have $g = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g)$.

@@

\begin{corollary}\label{cor:finite-rep-set}
	There is a (finite) set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
\end{corollary}

\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
Suppose that we are given a set $\V$ and finite minimum representative set $\V^*$ such that $g_\V = g_{\V^*}$.\jessie{Too much assumption}

@@

\begin{claim}\label{claim:vstar-supporting-G}
	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
	% \jessie{Notes in meeting:
	%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
	%   Argue $G \subseteq H^+_{v^*}$ by definition.
	%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
	%
	By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
	First, $G \subseteq H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
	Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
	$H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
	By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
	Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
\end{proof}

@@

	(1) $(x,g(x)) \in F_v$

	(2) $\inprod{v}{x}= g(x)$

@@

	For $1 \iff 4$, the forward implication follows trivially by applying the definition of the projection $\pi$.
	For the reverse implication, consider some $x \in \pi(F_v)$.
	There must be a $c \in \reals$ so that $(x,c) \in F_v$.
	Expanding, this is actually saying $(x,c) \in \{(x',c') \in G \mid \inprod{v}{x'} = c\}$.
	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g(x)$.
	Therefore, we have $(x, g(x)) \in F_v$.
\end{proof}

Now we can observe a set of normals generating facets whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	For $\V' \subseteq \V$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	We would like to show
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

	$\impliedby$
	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ for allwhen restricting to $x \in \reals_+^\Y$.
	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.

@@

For the set $\V^*$, we have each of these projected facets being full-dimensional in the projected space as well.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
\end{proof}

@@

Given a loss $L$ with $\risk L_+$ polyhedral, take $v = L(r)$ for any $r \in \R$.
As $H_{v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).

\begin{claim}\label{claim:faces-contained-in-facets}
	If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. 
\end{claim}
\begin{proof}
	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ and $F_v$ is not empty.
	Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.

>>>>

%\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
\jessiet{Revisit: definition of hyperplanes is not oriented}
\begin{definition}[Supports]
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	(i) $P \subseteq H^+$ or $P \subseteq -H^+$, and
	(ii)$H \cap \mathrm{bd}(P) \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \mathrm{bd}(P)$.
\end{definition}

@@

%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, 
  (i) there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, 
  (ii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$, and
  (iii) $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.	
	\citet[Proposition 4.5(i)]{gallier2008notes} can then be applied to yield the existence of a unique finite set of closed halfspaces $\H^*$ uniquely determining $P$. (i)
	Additionally, (iii) is shown by~\citep[Proposition 4.5(ii)]{gallier2008notes}.

	It is just left to show (ii).
	Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that $H_{(w,b)}$ uniquely determines a facet of $P$.
	The result then follows if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
	As halfspaces are uniquely determined, this is only true if some $H_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
	\jessiet{This is super hand-wavy, and not nearly as precise as I'd like, but it's a first pass.}
  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
\end{proof}

@@

Given any $v$ in a given set $\V$, define $H^+_v := H^+_{(v, -1)}$, where $(v, -1)\in\reals^\Y_+\times\reals$ define a halfspace.
Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict our $\hyp(g_\V)$ to the nonnegative orthant. 
Similarly, we let $H_v := H_{(v,-1)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$.

%Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
Finally, given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
If $\V$ is understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

@@

Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
Now, we can define $G$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
\begin{claim}\label{claim:G-intersection-H}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
  Then $G = \cap \H$.
\end{claim}
\begin{proof}
  $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$ respectively, so $(x,c) \in \cap \H$.
\end{proof}

@@

\begin{claim}\label{claim:G-full-dimensional}
  Given a finite, nonempty set $\V \subset \reals^d$ and $G := \hyp(g_\V)$, $G$ is $d$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
\end{claim}
\begin{proof}
  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
\end{proof}

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet.
\end{lemma}
\begin{proof}
  Since $G$ is full-dimensional by Claim~\ref{claim:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}
We can also show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $G$.

\begin{lemma}\label{lem:HY-subset-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, consider the unique set $\H^* \subseteq (\H_\V \cup \H_\Y)$ such that $\hyp(g_\V) = \H^*$.
  Then $\H_\Y \subseteq \H^*$.
\end{lemma}
\begin{proof}
  If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$ and is concave.
  Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
\end{proof}

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the smallest unique set $\H^*$ such that $\hyp(g_\V) =: G = \cap \H^*$.
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
  Take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ to be the unique set generating $\H_{\V^*}$.
  (Uniqueness of $\V^*$ follows from uniqueness of $\H^*$.)
  The moreover follows since every $H_v \in \H_{\V^*} \subseteq \H^*$ generates a facet.

@@

\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
  Let $\V' \subset \reals^\Y_+$ be a finite set such that $\H := \H_\Y \cup \H_{\V'}$ satisfies $\hyp(g_\V') = \cap \H$, and take $\V^*$ the unique set such that $\H^* = \H_\Y \cup \H_{\V^*}$.  
  Then $\V^* \subseteq \V'$.
\end{corollary}
\begin{proof}
  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V'}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V'$.
\end{proof}

We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$.
\begin{claim}\label{claim:g-gen-by-Vstar}
	Given a finite set $\V$, consider the minimum set $\V^* \subseteq \V$ such that $\hyp(g_\V) = \hyp(g_{\V^*})$.
  $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
\end{claim}
\begin{proof}
  $\hyp(g_\V) = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
  Since $G$ is the hypograph of $g_\V$, this means $g_\V$ can be written as 
  $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
\end{proof}

@@

Now suppose $L$ is a minimizable loss function.
For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$, which we assume is polyhedral throughout.
Consider the function $g(x) = \risk{L}_+(x)$.
%As before, take $G$ to be the hypograph of $g$.
We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  
Unlike above, these could be infinite sets.  
Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
\begin{claim}
	$\hyp(g_\V) = \cap\H$.
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_\V)
	&\iff g_\V(x) \geq c & \text{ Definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
	& & \text{the inner product with $x$ and minimizable.} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$} \\ 
	\end{align*}
	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g_\V) = \cap \H$.

@@

%\raf{Need to use minimizable}
We can now use the results from \S~\ref{appsubsec:phase1} to conclude that $\hyp(g_\V)$ has a unique minimum halfspace representation $\cap \H^*$, where $\H^* = \H_\Y \cup \H_{\V^*}$ for the unique finite set $\V^*$.
Moreover, we have $g_\V = g_{\V^*}$, as $\H^*$ is the unique minimum halfspace representation for $\hyp(g_\V)$.

@@

\begin{corollary}\label{cor:finite-rep-set}
	Given a minimizable loss $L : \R \times \Y \to \reals$ with polyhedral extended Bayes risk $\risk L_+$, take $L(\R) = \V$ and $\V^*$ to be the unique minimum set such that $\hyp(g_{\V}) = \cap (\H_\Y \cup \H_{\V^*})$.
	There is a (finite) set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
\end{corollary}

\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
Suppose that we are given a set $\V$ and the unique finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.

@@

\begin{claim}\label{claim:vstar-supporting-G}
	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G := \hyp(g_\V)$ at $(x,g_\V(x))$.
\end{claim}
\begin{proof}
	% \jessie{Notes in meeting:
	%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
	%   Argue $G \subseteq H^+_{v^*}$ by definition.
	%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
	%
	By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g_\V(x) = g_{\V^*}(x) = \min_{v \in \V^*}\inprod{v}{x}$.
	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
	First, $G \subseteq H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
	Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
	$H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
	By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
	Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
\end{proof}

@@

	(1) $(x,g_\V(x)) \in F_v$

	(2) $\inprod{v}{x}= g_\V(x)$

@@

	For $1 \iff 4$, the forward implication follows trivially by applying the definition of the projection $\pi$.
	For the reverse implication, consider some $x \in \pi(F_v)$.
	There must be a $c \in \reals$ so that $(x,c) \in F_v$.
	Expanding, this is actually saying $(x,c) \in \{(x',c') \in \hyp(g_\V) \mid \inprod{v}{x'} = c\}$.
	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g_\V(x)$.
	Therefore, we have $(x, g_\V(x)) \in F_v$.
\end{proof}

Now we can observe a set of normals generating facets whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	For $\V' \subseteq \V$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	We would like to show
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

	$\impliedby$
	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.

@@

For the set $\V^*$, we have each of these projected facets being full-dimensional in the projected space as well.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
\end{proof}

@@

Given a loss $L$ with $\risk L_+$ polyhedral and $\V = L(\R)$, take $v = L(r)$ for any $r \in \R$.
As $H_{v}^+ \in \H$, it supports $\hyp(g_\V)$ or it is redundant in $\H$ (or both).

\begin{claim}\label{claim:faces-contained-in-facets}
	Given $\V \subseteq \reals^\Y$ satisfying the above requirements, if a $H_v \in \H$ supports $\hyp(g_\V) =: G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. 
\end{claim}
\begin{proof}
	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ and $F_v$ is not empty.
	Since $H^+_v$ is valid, we have $F_v = F_{(v,-1)}$ is a face by definition.
